\chapter{Literature Review}\label{sec3}
\thispagestyle{empty}

%https://www.bis.org/publ/qtrpdf/r_qt2412b.pdf


\section{Foundations of Sentiment Analysis in Finance}

While the application of sentiment analysis in banking supervision is a relatively new field, \cite{debondt1985} and \cite{cutler1988} already showed that financial markets react to news. \cite{debondt1985} show that they do not only react but tend to overreact to unexpected and dramatic news events. \cite{tetlock2007} was one of the first which constructed a quantitative indicator based on news article sentiment to analyse the interactions between news articles and the stock market by using a bag-of-words algorithm. The results show that high media pessimism predicts falling stock prices. \cite{du2024} show that most literature focuses on applications in predictive analytics for financial metrics such as asset prices or the corresponding volatility. Applications mainly include investment management, with coverage of the stock market, foreign exchange market, and cryptocurrency market.
% eventuell noch schiller und kahneman & tversky?

\section{Sentiment Analysis for Banking Supervision}

While research in financial sentiment analysis methods often focuses on the investment decision-making process, they may also have potential applicability in the context of banking supervision. The body of literature directly related to sentiment analysis in banking supervision remains limited. Hence, we also cover studies of sentiment analysis for general financial distress prediction, which could easily be applied to the banking sector specifically. Following \cite{kearney2014}, we categorise the sentiment analysis for banking supervision literature according to their corresponding data source to corporation-expressed sentiment, media-expressed sentiment and internet-expressed sentiment. \\

Corporation-expressed sentiment analysis tries to capture the tone of the corporate executives regarding the performance, management and the strategy of a firm based on various corporate disclosures. \cite{hajek2023} and \cite{huang2023} show that the predictive performance of general financial distress prediction methods for firms can be improved by extending them with sentiment measures which are based on firms' annual reports. By analysing the U.S. banking sector, \cite{gandhi2019} suggests that the early warning systems of banking supervision authorities which are based on financial statement data could be extended by an indicator derived from the frequency of negative words in the banks' annual reports. While these studies focus on classifying the sentiment of text, \cite{hajek2023} show that speech emotion recognition can be applied on transcripts of earning conference calls and show that managerial emotions recognition can improve financial distress prediction. \\
% more https://www.doi.org/10.1109/SSCI.2016.7850006, \cite{nopp2015}

 Focusing on content published by news agencies, media-expressed sentiment tries to capture the tone in a news article. \cite{smales2016} analyses the media-expressed sentiment on banks using news sentiment data from Thomson Reuters News Analytics (TRNA). The algorithm used by TRNA identifies all sentences where the corresponding bank is mentioned and analyses the related content. The algorithm considers the order of words, adjectives, and common financial expressions. It is trained using several thousand randomly selected news stories which were manually labeled by former market participants \citep{smales2016}. TRNA classifies each story as negative, neutral or positive. \cite{smales2016} computed the sentiment indicator by summing up the classified sentiment of all novel, highly-relevant news stories for the bank considered, whereby negative stories have a score of -1, neutral stories of 0 and positive stories of 1. \cite{smales2016} uses a sample of major international banks for the observation period from the first of November 2004 until the 31st of December 2010. The results of \cite{smales2016} suggest that while Credit Default Swap (CDS) spreads as a marked determined measure react to news sentiment, the spread between the London Interbank Offered Rate (LIBOR) and Overnight Indexed Swaps (OIS) as a bank determined measure does not. Furthermore, by analysing the relationship between the sentiment of certain news topics and CDS spreads, the studies of \cite{roeder2020} suggest that further categorising news sentiment into topics might improve the predictive power of the indicator. They use sentiment scores and topic classifications by RavenPack News Analytics for a sample of systemically important banks which are tracked in the KBW Nasdaq Global Bank Index. The observation period spans from the first of January 2009 until the 31st of May 2018. Both \cite{smales2016} and \cite{roeder2020} show that negative sentiment in news articles could indicate higher risk of the corresponding bank. However, as \cite{agoraki2022} note, positive sentiment can also lead to increased financial instability by increased risk appetite by bank investors. \cite{borovkova2017} extend the sample to systemically important financial institutions and show that an indicator for systemic risk constructed from news sentiment leads other systemic risk measures by as long as 12 weeks. \\
% https://doi.org/10.21203/rs.3.rs-2305052/v1 (attention not peer reviewed)
 
 Internet-expressed sentiment tries to capture the tone of the discussion in social media posts which can be written by the bank itself, public or private institutions or natural persons. \cite{fernandez2021} derive a sentiment indicator for the Mexican financial sector as a whole based on tweets, which captures sources of financial stress which are not reflected in quantitative risk measures and show that this indicator correlates with measures for financial risk. \cite{illia2021} analyse the relationship between the sentiment of tweets about a single bank and its daily business performance and find that tweet sentiment might affect bank performance when embedded in a larger conversation. The recent banking crisis in 2023 opened the discussion whether social media is a new factor which accelerates bank run behavior. Indeed, by analysing the bank run on Silicon Valley Bank in 2023, first results in \cite{cookson2023} indicate that social media sentiment could amplify bank run risk.
% \cite{mendoza2024}
% https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=10648688
% https://www.sciencedirect.com/science/article/pii/S0378426620302314

\section{Measures for Financial Distress of Banks}

Since the riskiness of a bank cannot be measured directly, the empirical literature about financial distress of banks relies on indirect measures. Hence, different measures have been developed in the literature which should proxy the health of a bank. Some measures rely on accounting data of the corresponding banks. For example, \cite{sinkey1978} addresses the question of identifying problematic banks and observes that nearly all failed banks exhibited low net capital ratios. However, most banks with low net capital ratios did not fail. Other studies such as \cite{chiaramonte2016} analyse the predictive performance of the Altman Z-score in the banking sector. The main limitation of such measures is the relative low frequency due to the dependency on accounting data. Market measures in contrast are available in higher frequency and hence enable nowcasting the risk of banks. Market measures are derived from financial markets such as the stock or options market and try to get an implied proxy of the perceived risk of market participants. \cite{sarin2016} give an overview of market measures such as stock price volatility, option implied volatility, credit default swaps, the price to earnings ratio and preferred stock yields. They state that all indicators are only an imperfect proxy but looking at multiple different indicators enables the assessment of market beliefs.

%\begin{itemize}
%	\item \cite{coffinet2013}
%	\item \cite{avino2019}
%\end{itemize}
%
%Das muss unbedingt noch irgenwo rein (aus \cite{sarin2016}):
%It is noteworthy that, as Jeremy Bulow and Paul Klemperer (2013, 2015) and Andrew Haldane (2014) point out, measures of regulatory capital have historically not had much predictive power for bank failures.
% finde das irgendwie nicht so deutlich in diesen quellen... evtl besser doch weglassen


\section{Contribution to the Literature}

This study builds on existing studies about explaining and predicting risk proxies of banks. First, we test whether news sentiment is an additional determinant of CDS spreads. \cite{annaert2013} analysed the determinants of CDS spreads for 32 banks in the Euro area for the observation period spanning from December 2003 to September 2010. We extend this model by adding a news sentiment indicator and evaluate the model for European Globally Systematically Important Banks (G-SIBs) for the observation period from September 2023 to October 2024 as well as for UBS and Credit Suisse from January 2022 to June 2023. Next, we modify the model to predict CDS spreads for sovereign debt by \cite{cathcart2020} to be suitable for banks and evaluate the results on the same sample as before. Additionally, we take up the research question of \cite{roeder2020} and test whether we can confirm the significant effect of non-financial news sentiment on CDS spreads using our sample. Compared to the studies by \cite{smales2016} or \cite{roeder2020}, we do not use sentiment scores provided by an external sources but rather leverage LLMs to construct the sentiment scores by ourselves. Additionally to the analysis of CDS spreads, we evaluate the predictive power of news sentiment for stock price decreases as well as stock price volatility. To the best of our knowledge, this is the first study to examine the construction of a sentiment indicator based on Swiss news articles using LLMs to be applied for measuring idiosyncratic risks of Swiss banks. 


%In addition to several simpler independent models, the model for analysing the determinants of CDS spreads from \cite{annaert2013} is extended by a news sentiment indicator, the model to predict CDS spreads for sovereign debt by \cite{cathcart2020} is modified to be suitable for banks and the research question of \cite{roeder2020} is analysed. The sentiment indicator is constructed for Swiss banks for an observation period from January 2022 to June 2023, hence including the Credit Suisse collapse, as well as for European G-SIBs for an observation period from September 2023 to October 2024. The study is designed in the perspective of financial supervision.

\cleardoublepage
